Flowchart of Current Algorithm

### 2012-01-22 docs/flowchart/flowchart.tex
add thermal diffusion to flowchart

%-----------------------------------------------------------------------------
% graphical flowcharts
%-----------------------------------------------------------------------------
\begin{figure}[tb]
\centering
\includegraphics[scale=0.75]{\flowfigpath/flowchart}
\caption[Graphical flowchart of MAESTRO]
  {\label{Fig:flowchart} A flowchart of the algorithm.  The
  thermodynamic state variables, base state variables, and local velocity are
  indicated in each step.  Red text indicates that quantity was
  updated during that step.  The predictor-corrector steps are
  outlined by the dotted box.  The blue text indicates state
  variables that are the same in {\bf Step 6} as they are in
  {\bf Step 2}, i.e., they are unchanged by the predictor steps.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tb]                                               
\centering
\includegraphics[scale=0.75]{\flowfigpath/flowchart_4_8}
\caption[Graphical flowchart of the density and enthalpy update steps]
{\label{Fig:flowchart48} A flowchart for {\bf Steps 4} and {\bf 8}.
  The thermodynamic state variables and base state variables are
  indicated in each step.  Red text indicates that quantity was
  updated during that step.  Note, for {\bf Step 4}, the updated
  quantities should also have a $\star$ superscript, e.g., {\bf Step
    8I} defines $T^{(2)}$ while {\bf Step 4I} defines $T^{(2),\star}$
  .}
\end{figure}

>>>>

%-----------------------------------------------------------------------------
% graphical flowcharts
%-----------------------------------------------------------------------------
\begin{figure}[tb]
\centering
\includegraphics[scale=0.65]{\flowfigpath/flowchart}
\caption[Graphical flowchart of MAESTRO]
  {\label{Fig:flowchart} A flowchart of the algorithm.  The
  thermodynamic state variables, base state variables, and local velocity are
  indicated in each step.  Red text indicates that quantity was
  updated during that step.  The predictor-corrector steps are
  outlined by the dotted box.  The blue text indicates state
  variables that are the same in {\bf Step 6} as they are in
  {\bf Step 2}, i.e., they are unchanged by the predictor steps.
  The diffusion steps (4a and 8a) are optional, depending on
  {\tt use\_thermal\_diffusion}.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tb]                                               
\centering
\includegraphics[scale=0.75]{\flowfigpath/flowchart_4_8}
\caption[Graphical flowchart of the density and enthalpy update steps]
{\label{Fig:flowchart48} A flowchart for {\bf Steps 4} and {\bf 8}.
  The thermodynamic state variables and base state variables are
  indicated in each step.  Red text indicates that quantity was
  updated during that step.  Note, for {\bf Step 4}, the updated
  quantities should also have a $\star$ superscript, e.g., {\bf Step
    8I} defines $T^{(2)}$ while {\bf Step 4I} defines $T^{(2),\star}$
  .}
\end{figure}
